---
title: "Chick Weight Analysis"
author: "Amjad Altuwayjiri"
date: "03/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)

keep <- packages[!(packages %in% installed.packages()[,"Package"])]

if(length(keep)) {
  install.packages(keep)
}

```

## Descriptive Statisticst.

This study shows the effect of the type of food on the chicken wight. The type of food has been tested are:casein, horsebean, linseed, meatmeal, soybean and sunflower.

   


```{r chickwts, echo= FALSE}

chickwts %>% 
  group_by(feed) %>%
  summarise(n = length(feed),
            average = mean(weight), 
            SD = sd(weight)) 


```

## Plots


```{r boxplot, echo=FALSE}
ggplot(chickwts, aes(x = feed, y = weight)) +
  geom_jitter() +
  stat_summary(fun.data = mean_sdl,
               fun.args = list(mult = 1),
               col = "red")

ggplot(chickwts, aes(x = feed, y = weight)) +
   geom_boxplot()
```



## Inferential Statistics

```{r ANOVA, echo=FALSE}
chickwts_lm <- lm(weight ~ feed, data = chickwts)
chickwts_lm
#1- way anova
anova(chickwts_lm)
```

## Over all view 

```{r results echo=FALSE }
chickwts.av <- aov(weight ~ feed, data = chickwts)
tukeyTest <- TukeyHSD(chickwts.av)
datatable(tukeyTest$feed)
chickwts.av
tukeyTest


